---
title: "measuring arduino vcc internally"
output: html_document
---

The supply voltage was measured by the following code.

```
long readVcc() {
  long result;
  // Read 1.1V reference against AVcc
  ADMUX = _BV(REFS0) | _BV(MUX3) | _BV(MUX2) | _BV(MUX1);
  delay(2); // Wait for Vref to settle
  ADCSRA |= _BV(ADSC); // Convert
  while (bit_is_set(ADCSRA,ADSC));
  result = ADCL;
  result |= ADCH<<8;
  result = 1126400L / result; // Back-calculate AVcc in mV
  return result;
}

void setup() {
    Serial.begin(9600);

}

// the loop function runs over and over again forever
void loop() {
    Serial.print(millis());
    Serial.print(",");
    Serial.println(readVcc());
    delay(1000);
}
```

This is from an answer in the post below.

[analogread - How to measure the supply voltage of Arduino without using an analog pin - Arduino Stack Exchange](https://arduino.stackexchange.com/a/50771/43776)

The results of `Serial.print()` was copied to `vcc.txt` and analysed as follows.

```{r}
dat <- read.table("vcc.txt", sep=":")
vcc <- data.frame(t=dat$V1/1000, v=dat$V2/1000)
library(ggplot2)
  qplot(vcc$t, vcc$v) +
  geom_point() +
  ylim(4, 5) +
  xlab("time [s]") +
  ylab("AVcc [V]")

```

The mean voltage was `r mean(vcc$v)` [V]. 4.501 [V]. The voltage measured by a digital multimeter was 4.49 [V] so the magic number was corrected as $1024 * 1.1 * 4.49 / 4.501 = 1124$. 

AVcc was measured and analysed again in the same manner. The result is in `vcc1124.txt`.

```{r}
dat <- read.csv("vcc1124.txt", header=F)
vcc <- data.frame(t=dat$V1/1000, v=dat$V2/1000)
library(ggplot2)
qplot(vcc$t, vcc$v) +
  geom_point() +
  ylim(4, 5) +
  xlab("time [s]") +
  ylab("AVcc [V]")

```

```{r}
ggplot(vcc, aes(x = v)) +
  geom_histogram()
```

AVcc was `r mean(vcc$v)` +/- `r sd(vcc$v)` [V].


